candidate genes

### 2019-12-15 analysis/10_specificgenes.Rmd
stil working on colors

x <- correlate(counts)
rplot(x, colors = c("skyblue1", "white", "indianred2"))  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

>>>>

x <- correlate(counts)

rplot(x, colors = c("skyblue1", "white", "indianred2"))  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitletitle = "inc.d9 to inc.d17")
